---
title: "DS-283: Webrender Nightly Dashboard"
author: "Managed by Data Science,`r sprintf(' rendered at %s PST',Sys.time())`"
output:
  html_document:
    toc: false
    toc_depth: 5
---



<style>
@import url("https://fonts.googleapis.com/css?family=Nunito|Quattrocento+Sans|Roboto+Mono:300&display=swap");
body {
    line-height: 1.4em;
    font-family: 'Quattrocento Sans', sans-serif;
    background-color: transparent;
    }
    

.r {
    background-color: white;
    border: 0;
        }
        
h4 { 
    background-color: #EEF1E6; 
}

.author {
    background-color: transparent;
}

pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}

h1,h2,h3,h4,h5,h6 {
    font-family: 'Nunito', sans-serif;
}

table {
font-family: 'Roboto Mono', monospace;
font-size: 85%;
}

pre,code {
    border:0;
    font-family: 'Roboto Mono', monospace;
    font-size: 80%;
}

ul.navtabs !{
    border:0;
}

p.caption {
    font-weight: bold;
}

p.caption ol,li {
    font-weight: bold;
}


.figure {
    text-align: center;
    width: 80vw;
    position: relative;
    margin-left: calc((100% - 80vw)/2);
}


</style>



```{r echo=FALSE,warning=FALSE, results='hide',message=FALSE,message=FALSE}
library(knitr)
knitr::opts_chunk$set(  cache=FALSE,echo=FALSE,warning=FALSE,message=FALSE,eval=FALSE,fig.width=13,fig.height=4)
source("query.R")
#g <- bq()

```


This is dashboard comparing Webrender vs Non Webrender via a Normandy
experiment. The population targeted is Windows-10 Nightly platforms with Intel
graphics cards. For more details read the [JIRA ticket](https://jira.mozilla.com/browse/DS-283) and the [Experimenter Page](https://experimenter.services.mozilla.com/experiments/webrender-continued-v2-nightly-only/).

_Use your mouse to hover over areas on the graph for more information on the `buildid`. You can also use the
scroll on the mouse pad to zoom into the figure. Double click the figure to reset._

Information for builds till `r g$q("select max(buildid) as V from {ds_283_tablename}")$V`.


```{r eval=TRUE}


W <- 1000; H <- 200;
```


##  {.tabset}




### Performance

####  CONTENT_FRAME_TIME_VSYNC

```{r eval=TRUE,fig.cap='Fig1. Probabilty CONTENT_FRAME_TIME_VSYNC >= 200'}

content_frame_time_vsync.plot  <- create.figure(LL="content_frame_time_vsync_200",title="",
                                                yaxislab='Proportion',width=W,height=H,
                                                bqtable=ds_283_tablename, g=g)
vw(content_frame_time_vsync.plot)

```


&nbsp;
&nbsp;
&nbsp;

#### FX_TAB_SWITCH_COMPOSITE_E10S_MS

```{r eval=TRUE,fig.cap='Fig2. Average FX_TAB_SWITCH_COMPOSITE_E10S_MS'}

tab_switch_ms.plot  <- create.figure(LL="tab_switch_ms",title="",
                                                yaxislab='ms',width=W,height=H,
                                                bqtable=ds_283_tablename, g=g)
vw(tab_switch_ms.plot)

```


&nbsp;


#### FX_PAGE_LOAD_MS2
```{r eval=TRUE,fig.cap='Fig3. Average FX_PAGE_LOAD_MS2'}

page_load_ms.plot  <- create.figure(LL="page_load_ms",title="",
                                                yaxislab='ms',width=W,height=H,
                                                bqtable=ds_283_tablename, g=g)
vw(page_load_ms.plot)

```

&nbsp;



#### CONTENT_FULL_PAINT_TIME

```{r eval=TRUE,fig.cap='Fig4. (a) Average CONTENT_FULL_PAINT_TIME and (b) Probability CONTENT_FULL_PAINT_TIME>=16ms(b)'}

content_full_paint_time.plot  <- create.figure(LL="content_full_paint_time",title="(a) Average CONTENT_FULL_PAINT_TIME",
                                              yaxislab='ms',width=W/1.85,height=H,
                                              bqtable=ds_283_tablename, g=g,LA=90)

content_full_paint_time_16.plot  <- create.figure(LL="content_full_paint_time_16",title="(b) Prob(CONTENT_FULL_PAINT_TIME>=16)",
                                              yaxislab='',width=W/1.85,height=H,
                                              bqtable=ds_283_tablename, g=g,LA=90)

vw(list(
    config = list( legend = list(direction='horizontal',orient='top',title=NULL)),
    hconcat = list(
          content_full_paint_time.plot,
          content_full_paint_time_16.plot
      )),TRUE)

```


&nbsp;

#### CONTENT_PAINT_TIME

```{r eval=TRUE,fig.cap='Fig5. (a) Average CONTENT_PAINT_TIME, (b) Probability CONTENT_PAINT_TIME>=16ms, and (c) 99 Percentile CONTENT_PAINT_TIME'}

content_paint_time.plot  <- create.figure(LL="content_paint_time",title="(a) Avg. CONTENT_PAINT_TIME",
                                              yaxislab='ms',width=W/1.85,height=H,
                                              bqtable=ds_283_tablename, g=g,LA=90)


content_paint_time_16.plot  <- create.figure(LL="content_paint_time_16",title="(b) Prob(CONTENT_PAINT_TIME>=16)",
                                              yaxislab='',width=W/1.85,height=H,
                                              bqtable=ds_283_tablename, g=g,LA=90)
content_paint_time_99p.plot  <- create.figure(LL="content_paint_time_99",title="(c) 99 Percentile CONTENT_PAINT_TIME",
                                              yaxislab='',width=W/1.85,height=H,
                                              bqtable=ds_283_tablename, g=g,LA=90)

vw(list(
    config = list( legend = list(direction='horizontal',orient='top',title=NULL)),
    vconcat=list(
            list(
                hconcat = list(
                    content_paint_time.plot,
                    content_paint_time_16.plot
                )),
            content_paint_time_99p.plot
        )
        ) ,TRUE)
```

&nbsp;

#### COMPOSITE_TIME

```{r eval=TRUE,fig.cap='Fig6. (a) Average COMPOSITE_TIME and (b) Probability COMPOSITE_TIME>=16ms'}

composite_time.plot  <- create.figure(LL="composite_time",title="(a) Average COMPOSITE_TIME",
                                              yaxislab='ms',width=W/1.85,height=H,
                                              bqtable=ds_283_tablename, g=g,LA=90)

composite_time_16.plot  <- create.figure(LL="composite_time_16",title="(b) Prob(COMPOSITE_TIME>=16)",
                                              yaxislab='',width=W/1.85,height=H,
                                              bqtable=ds_283_tablename, g=g,LA=90)

vw(list(
    config = list( legend = list(direction='horizontal',orient='top',title=NULL)),
    hconcat = list(
             composite_time.plot,
             composite_time_16.plot
      )),TRUE)

```

&nbsp;

#### CONTENT_FRAME_TIME

```{r eval=TRUE,fig.cap='Fig7. Probability CONTENT_FRAME_TIME>=192% vsync'}


content_frame_time_192.plot  <- create.figure(LL="content_frame_time_192",title="",
                                              yaxislab='',width=W,height=H,
                                              bqtable=ds_283_tablename, g=g)

vw(content_frame_time_192.plot,TRUE)

```

&nbsp;


#### Severe Checkerboarding

```{r eval=TRUE,fig.cap='Fig8. Severe Checkerboarding Events/1000 HR'}

checker <- create.figure(LL="severe_checkerboard_perkhr",title="",
                    yaxislab='Estimate(Per 1000 Hours)',width=W,height=H,
                    bqtable=ds_283_tablename, g=g)
vw(checker)
```



### Stability



#### Crash Rate/Likelihood : ALL And Device Resets
```{r eval=TRUE,fig.cap='Fig9. (a) Crash Rate (ALL) Per Profile Per 1000 Hrs (b) Proportion Profiles Crashing (ALL)'}


mc <- create.figure(LL="ncrash_all_perkhr",title="(a) Crash Rate (ALL) Per Profile Per 1000 Hrs",
                    yaxislab='Estimate',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)
mci <- create.figure(LL="ncrash_all_inci",title="(b) Proportion Profiles Crashing (ALL)",
                    yaxislab='Proportion',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)
vw(list(
    config = list( legend = list(direction='horizontal',orient='top',title=NULL)),
    hconcat = list(
             mc,mci
         )
        ),TRUE)

```


```{r eval=TRUE,fig.cap='Fig10. (a) Device Reset/Profile/1000 Hrs (b) Proportion of Profiles with Device Resets'}

dr <- create.figure(LL="crash_device_resets_perkhr",title="(a) Device Reset Rate  Per Profile Per 1000 Hrs",
                    yaxislab='Estimate',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)

dri <- create.figure(LL="device_reset_inci",title="(b) Proportion Profiles With Device Resets",
                    yaxislab='Proportion',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)
vw(list(
    config = list( legend = list(direction='horizontal',orient='top',title=NULL)),
    hconcat = list(
             dr,dri
      )),TRUE)
```

#### Crash Rates: Detail (OOM,GPU,Content, Main)

```{r eval=TRUE,fig.cap='Fig11. (a) Content, (b) Main, (c) GPU, and (d) OOM Crash Rates(/Profile/1000 Hrs)'}

ccr <- create.figure(LL="ncrash_content_perkhr",title="(a) Content Crash Rate/Profile/1000 Hrs",
                    yaxislab='Estimate',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)

cmr <- create.figure(LL="ncrash_main_perkhr",title="(b) Main Crash Rate/Profile/1000 Hrs",
                    yaxislab='Estimate',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)

cgr <- create.figure(LL="ncrash_gpu_perkhr",title="(c) GPU Crash Rate/Profile/1000 Hrs",
                    yaxislab='Estimate',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)

 cor <- create.figure(LL="ncrash_oom_perkhr",title="(d) OOM Crash Rate/Profile/1000 Hrs",
                    yaxislab='Estimate',width=W/1.85,height=H,
                    bqtable=ds_283_tablename, g=g,LA=90)

vw(list(
    config = list( legend = list(direction='horizontal',orient='top',title=NULL)),
    vconcat=list(
            list(hconcat = list( ccr,cmr)),
            list(hconcat = list( cgr,cor))
        )
        ) ,TRUE)

```


### Usage


```{r eval=TRUE,fig.cap='Fig12. Active Hours/Profile While on Build'}

ah <- create.figure(LL="active_hours",title="",
                    yaxislab='Hours',width=W,height=H,
                    bqtable=ds_283_tablename, g=g)
vw(ah)
```


```{r eval=TRUE,fig.cap='Fig13. Total Hours/Profile While on Build'}
th <- create.figure(LL="total_hours",title="",
                    yaxislab='Hours',width=W,height=H,
                    bqtable=ds_283_tablename, g=g)
vw(th)

```{r eval=TRUE,fig.cap='Fig14. URIs/Profile/Active While on Build'}
uh <- create.figure(LL="uri_per_profile_activehour",title="",
                    yaxislab='Estimate',width=W,height=H,
                    bqtable=ds_283_tablename, g=g)
vw(uh)


```


### Enrollments


```{r eval=TRUE,fig.cap='Fig 15. Client Enrollments Across Builds'}

enrolls <- g$q("select * from {ds_283_tablename} where label='enrollement_status' order by buildid, what",-1)
enrolls <- enrolls[, list(Branch=what, buildid=buildid, Enrolled = nreporting)]
enrolls <- enrolls[, buildid := parse_date(buildid)]
enrolls <- enrolls[Branch=='enabled',  buildid2 := format_iso_8601(buildid-as.difftime(0,units='mins'))]
enrolls <- enrolls[Branch=='disabled', buildid2 := format_iso_8601(buildid+as.difftime(0,units='mins'))]

enroll.plot <- list(
        `$schema` = vega_schema(),
    data = list(values = enrolls),
        title = list(text="", anchor='start',fontWeight = 'normal'),
        width = W,
        height = H,
        autosize = list(type='fit',contains='content'),
        layer = list(            
            list(
                selection = list(
                    grid = list(type= "interval", bind="scales")
                ),
                mark = list(type="line",point='true'), #'transparent'), #,filled=TRUE),
                encoding = list(
#                    size = list(value=65),
                    x = list(field="buildid2",type='temporal',timeUnit="yearmonthdatehoursminutes",
                             axis=list(title="BuildIDs on this Date",titleFontWeight='light',
                                       tickExtra=FALSE,
                                       #tickCount=length(unique(xx$buildid)),
                                       grid=FALSE,labelOverlap='parity', format='%Y%m%d', labelAngle=360),
                             scale= list(type= "utc")
                             ),
                    y = list(field="Enrolled",
                             type="quantitative",axis=list(title="Enrolled Clients",grid=TRUE,
                                                           titleFontSize=11)),
                    color = list(field = "Branch", type = "nominal",scale=list(scheme="set1"),
                                 legend = list(direction='horizontal',orient='top',title=NULL)
                                 ),
                    tooltip=list(list(field = "buildid",type="nominal"),
                                 list(field = 'Branch', type='ordinal'),
                                 list(field = 'Enrolled', type='quantitative')
                                 )
                ))
        )
)

vw(enroll.plot)
```



### About

The sample size is not enough to detect small changes but choosing more would
use up all the appropriate population. This experiment will continue to enroll for
about a year.


#### ETL

The etl step runs everyday. The table `r ds_283_tablename` is read and those buildids that have
less than `r SEVEN`  days of data are updated. We only use three first `r SEVEN`
days since a  build
is released to estimate results for that build. For these builids we retrieve
performance, stability and usage data from `telemetry.main` (see code [here](https://github.com/mozilla/webrender_intel_win10_nightly/blob/master/driver.Rmd#L136)).

The etl also does the summarization. For usage information we compute means and
bootstrap intervals across the observation period (at most D says) for both
branches. Relative differences with respect to “disabled” are also computed

We do the same for crash information.

All metrics are per client and each client has the same weight.

Code for the above can be viewed
[here](https://github.com/mozilla/webrender_intel_win10_nightly/blob/master/driver.Rmd#L156)
and [here](https://github.com/mozilla/webrender_intel_win10_nightly/blob/master/driver.Rmd#L229).

For histograms, we follow the GLAM approach. That is we aggregate a clients
responses for a given histogram to one response (add all values for same bucket
for that client). This is then normalized to a density (convert sums to
proportions that sum to 1). These densities are averaged across clients. Under a
certain set of assumptions we can use these calculations to arrive at means and
error bars (see appendix).  The average density across clients is the
representative distribution of a typical histogram value for a typical client
. Note, this is the not the distribution of the average histogram response for a
client.

(There is one exception, checkerboard severity, where reduce the histogram to an average for a client)

Using this model for histograms, we compute the relevant statistics, relative
differences and their error bars. These are then uploaded to table `r ds_283_tablename`..

#### Dashboard

The dashboards is arranged in 3 tabs corresponding to performance, stability and
usage. Two lines one for each branch and each point corresponds to a build is

Hover over to see builid, value and error bar. The hover over also reveals the
relative difference and if this is followed by check mark then one can conclude
that there is sufficient evidence to conclude that branches are different.

You can zoom in with the mouse and doubl clock to reset.

The code for this is
[here](https://github.com/mozilla/webrender_intel_win10_nightly/blob/master/dashboard.Rmd).


#### Appendix

The file
[query.R](https://github.com/mozilla/webrender_intel_win10_nightly/blob/master/query.R)
contains all the functions.

If we have one observation, $X$ that can be one bucket out of $K$, we can model
this as a [Categorical Distribution](https://en.wikipedia.org/wiki/Categorical_distribution). 
We place a Dirichlet($1/K$) prior on the parameters and assuming every client
follows the same distribution, then the posterior is
Dirichlet($\sum p_1+1/K$\,$\sum p_2+1/K$,...,$\sum p_K+1/K$). Using this we can
get error bounds on estimates. 


