---
title: "DS-283: Webrender Nightly Dashboard GENERATION"
author: "Saptarshi Guha"
date: "`r Sys.Date()`"
output:
  html_document:
    mathjax: null
    toc: true
    toc_collapsed: false
    toc_depth: 5
    number_sections: true
    theme: cosmo
params:
    args: !r list()

---


<style>
body {
    line-height: 1.4em;
    width: 100%;
    }
.plotly {
    text-align: center;
    width: 75vw;
    position: relative;
    margin-left: calc((100% - 75vw)/2);
}
.zimg img {
    text-align: center;
    width: 75vw;
    position: relative;
    margin-left: calc((100% - 75vw)/2);
}
.r {
    background-color: white;
    border: 0;
        }
        
pre code, pre, code {
  white-space: pre !important;
  overflow-x: scroll !important;
  word-break: keep-all !important;
  word-wrap: initial !important;
}
.caption {
    font-size: 80%;
    font-style: italic;
    font-weight:bold;
        }

caption {
    font-size: 80%;
    font-style: italic;
    font-weight: bold;
        }

h3, .h3 {
    margin-top: 100px;
    }
    

</style>



```{r echo=FALSE,warning=FALSE, message=FALSE}

library(knitr)
knitr::opts_chunk$set(  cache=FALSE,echo=TRUE,warning=FALSE,message=FALSE,eval=FALSE,fig.width=13,fig.height=4)
source("query.R")

## args can have two params
## args(max.build.id = starting buildid, default is computed from existing table,
##      end.build.id = ending.build , default is yesterday
##      )

args <- params$args
is.debug <- if(!is.null(args$debug)) args$debug else FALSE
##g <- bq(path=args$path)

#args <- list(max.build.id='2020-04-01')
## is.debug <- TRUE
```


```{r f1,eval=TRUE}
```


This code will run every day. I don't want massive data pulls for old data. As
this is for nightly, we will 

- look up a database to see what was the last-build-id processed for
- get data for build-ids since then and now.
- you can provide your own via `max.build.id` (YYYYMMDD)

```{r eval=TRUE}

if(is.null(args$max.build.id)){
    max.build.id <-tryCatch({
        V <- g$q("select min(buildid) as V from {ds_283_tablename} where DATE_DIFF(date_computed,PARSE_DATE('%Y%m%d',buildid),DAY)<{SEVEN}")$V
        if(is.na(V)) stop()
        as.Date(V,'%Y%m%d')
    },error=function(e){
        experiment.start
    })
}else max.build.id <- as.Date(args$max.build.id,'%Y%m%d')
max.build.id <- as.Date(max.build.id)
loginfo(glue("Upto {max.build.id}"))
```

We get `r SEVEN` days of data for a `buildid`, however nearly 90% of the data
comes within 4 days of release (and about 50% within 1 day).

```{r eval=TRUE}

data.collection.dates <- local({
    if(!is.null(args$end.build)){
        end.date <- as.Date(args$end.build.id,'%Y%m%d')
    }else end.date <- Sys.Date()-1
    print(c("using end date",end.date))
    f <- data.table(buildid = seq(max.build.id,to=end.date,by=1))
    f[, ":="(start = buildid,end = buildid+SEVEN)]
    f[, ":="(buildid = strftime(buildid,"%Y%m%d"))]
    f[buildid >='20200401',]
})
print(data.collection.dates)

```

Now go ahead and get all the data for profiles. 

- in the [experiment](https://jira.mozilla.com/browse/DS-283?src=confmacro) 
- on these build-ids
- with data on  these dates

```{r query,eval=TRUE}

source("query.R")
#data.collection.dates[,count.avg.popln.size(buildid,start,end)]
new.data <- get.data(builds = data.collection.dates$buildid,
                     starts = data.collection.dates$start,
                     ends = data.collection.dates$end,
                     ds_283_tablename_tmp,
                     slug=slug
                     )
head(new.data)
```

Enrollment Status

```{r eval=TRUE}
(enrollment.status <- check.enrollment.status(ds_283_tablename_tmp))

```

Usage Length

```{r eval=TRUE}

compare.usage <- check.usage.length.and.crash(ds_283_tablename_tmp,
                                    starts = data.collection.dates$start,
                                    ends =  data.collection.dates$end)


Mean=mean
active.hours.cmp <- compare.usage[active_hours<quantile(active_hours,0.999),
                                  mAndCi(.SD[,list(id,branch,x=active_hours)], "x",REPLICATES,oper=Mean)
                                 ,by=buildid][, label := 'active_hours'][order(buildid,what),]
total.hours.cmp <- compare.usage[total_hours<quantile(total_hours,0.999),
                                  mAndCi(.SD[,list(id,branch,x=total_hours)], "x",REPLICATES,oper=Mean)
                                 ,by=buildid][, label := 'total_hours'][order(buildid,what),]
total.urisperhr.cmp <- compare.usage[total_uri/(1/3600+active_hours)<quantile(total_uri/(1/3600+active_hours),0.999),
                                  mAndCi(.SD[,list(id,branch,x=total_uri/(1/3600+active_hours))], "x",REPLICATES,oper=Mean)
                                 ,by=buildid][, label := 'uri_per_profile_activehour'][order(buildid,what),]



ncrash.all.cmp <- compare.usage[ncrash_all/(1/3600+total_hours)<quantile(ncrash_all/(1/3600+total_hours),0.999),
                                mAndCi(.SD[,list(id,branch,x=1000*ncrash_all/(1/3600+total_hours))], "x",REPLICATES,oper=Mean)
                               ,by=buildid][, label := 'ncrash_all_perkhr'][order(buildid,what),]

ncrash.content.cmp <- compare.usage[ncrash_content/(1/3600+total_hours)<quantile(ncrash_content/(1/3600+total_hours),0.999),
                                mAndCi(.SD[,list(id,branch,x=ncrash_content/(1/3600+total_hours))], "x",REPLICATES,oper=mean)
                               ,by=buildid][, label := 'ncrash_content_perkhr'][order(buildid,what),]
ncrash.content.cmp  <- ncrash.content.cmp [, ":="(est=est*1000,low=low*1000, high=high*1000)]

ncrash.main.cmp <- compare.usage[ncrash_main/(1/3600+total_hours)<quantile(ncrash_main/(1/3600+total_hours),0.999),
                                mAndCi(.SD[,list(id,branch,x=1000*ncrash_main/(1/3600+total_hours))], "x",REPLICATES,oper=Mean)
                               ,by=buildid][, label := 'ncrash_main_perkhr'][order(buildid,what),]

ncrash.shutdown.cmp <- compare.usage[ncrash_shutdown/(1/3600+total_hours)<quantile(ncrash_shutdown/(1/3600+total_hours),0.999),
                                mAndCi(.SD[,list(id,branch,x=1000*ncrash_shutdown/(1/3600+total_hours))], "x",REPLICATES,oper=Mean)
                               ,by=buildid][, label := 'ncrash_shutdown_perkhr'][order(buildid,what),]

ncrash.oom.cmp <- compare.usage[ncrash_oom/(1/3600+total_hours)<quantile(ncrash_oom/(1/3600+total_hours),0.999),
                                mAndCi(.SD[,list(id,branch,x=1000*ncrash_oom/(1/3600+total_hours))], "x",REPLICATES,oper=Mean)
                               ,by=buildid][, label := 'ncrash_oom_perkhr'][order(buildid,what),]

## notably this has no upper bound
ncrash.gpu.cmp <- compare.usage[ncrash_gpu/(1/3600+total_hours)<quantile(ncrash_gpu/(1/3600+total_hours),1),
                                mAndCi(.SD[,list(id,branch,x=1000*ncrash_gpu/(1/3600+total_hours))], "x",REPLICATES,oper=Mean)
                               ,by=buildid][, label := 'ncrash_gpu_perkhr'][order(buildid,what),]


device.reset.cmp <- compare.usage[device_resets/(1/3600+total_hours)<quantile(device_resets/(1/3600+total_hours),0.999),
                                mAndCi(.SD[,list(id,branch,x=device_resets/(1/3600+total_hours))], "x",REPLICATES,oper=Emean)
                               ,by=buildid][, label := 'crash_device_resets_perkhr'][order(buildid,what),]
device.reset.cmp  <- device.reset.cmp [, ":="(est=est*1000,low=low*1000, high=high*1000)]

checker.cmp <- compare.usage[checkerboard_severe_events/(1/3600+total_hours)<quantile(checkerboard_severe_events/(1/3600+total_hours),0.999),
                                mAndCi(.SD[,list(id,branch,x=checkerboard_severe_events/(1/3600+total_hours))], "x",REPLICATES,oper=Emean)
                            ,by=buildid][, label := 'severe_checkerboard_perkhr'][order(buildid,what),]
checker.cmp  <- checker.cmp [, ":="(est=est*1000,low=low*1000, high=high*1000)]

ncrash_all.inci.cmp <- compare.usage[, mAndCi(.SD[,list(id,branch,x=ncrash_all > 0)], "x",REPLICATES,oper=Mean)
                               ,by=buildid][, label := 'ncrash_all_inci'][order(buildid,what),]
device_resets.inci.cmp <- compare.usage[, mAndCi(.SD[,list(id,branch,x=device_resets > 0)], "x",REPLICATES,oper=Mean)
                               ,by=buildid][, label := 'device_reset_inci'][order(buildid,what),]


```



Now the histograms

1. CONTENT_FRAME_TIME_VSYNC

per cent frames exceeding 200% vsync. 

```{r content_frame_time_vsync,eval=TRUE}

content_frame_time_vsync.h <- histogram.aggregate.all("content_frame_time_vsync", table=ds_283_tablename_tmp)
content_frame_time_vsync.gt.200 <- histogram.summary.cuts(content_frame_time_vsync.h   ,CUT=200) 
(content_frame_time_vsync.gt.200 <- content_frame_time_vsync.gt.200 [, label := "content_frame_time_vsync_200"][,])

```

2. tab switch (fx_tab_switch_composite)

```{r fx.tab.switch.composite,eval=TRUE}

tab_switch_composite.h <- histogram.aggregate.all("tab_switch_ms",table=ds_283_tablename_tmp)
tab_switch_composite <- histogram.summary(tab_switch_composite.h)
(tab_switch_composite <- tab_switch_composite[, label := "tab_switch_ms"][,])

```

3. fx_page_load

```{r page_load_ms,eval=TRUE}

page_load_ms.h <- histogram.aggregate.all("page_load_ms",table=ds_283_tablename_tmp)
page_load_ms <- histogram.summary(page_load_ms.h)
(page_load_ms <- page_load_ms[, label := "page_load_ms"][,])

```

4. content_paint_full_time


```{r content_full_paint_time,eval=TRUE}

content_full_paint_time.h <- histogram.aggregate.all("content_full_paint_time",table=ds_283_tablename_tmp)
content_full_paint_time <- histogram.summary(content_full_paint_time.h)
(content_full_paint_time <- content_full_paint_time[, label := "content_full_paint_time"][,])

content_full_paint_time.gt.16ms <- histogram.summary.cuts(content_full_paint_time.h,CUT=16)
(content_full_paint_time.gt.16ms <- content_full_paint_time.gt.16ms[, label := "content_full_paint_time_16"][,])


```

5. content_paint_time

```{r content_paint_time,eval=TRUE}
content_paint_time.h <- histogram.aggregate.all("content_paint_time",table=ds_283_tablename_tmp)
content_paint_time <- histogram.summary(content_paint_time.h, REPLICATES.2)
(content_paint_time <- content_paint_time[, label := "content_paint_time"][,])

content_paint_time.99 <- histogram.summary.percentiles(content_paint_time.h,perc=0.99)
(content_paint_time.99 <- content_paint_time.99[, label := "content_paint_time_99"][,])

content_paint_time.gt.16ms <- histogram.summary.cuts(content_paint_time.h,CUT=16)
(content_paint_time.gt.16ms <- content_paint_time.gt.16ms[, label := "content_paint_time_16"][,])

```

6.composite_time

```{r composite_time,eval=TRUE}
composite_time.h <- histogram.aggregate.all("composite_time",table=ds_283_tablename_tmp)
composite_time <- histogram.summary(composite_time.h)
(composite_time <- composite_time[, label := "composite_time"][,])

composite_time.gt.16ms <- histogram.summary.cuts(composite_time.h,CUT=16)
(composite_time.gt.16ms <- composite_time.gt.16ms[, label := "composite_time_16"][,])

```


7. content_frame_time

```{r content_frame_time,eval=TRUE}
content_frame_time.h <- histogram.aggregate.all("content_frame_time",table=ds_283_tablename_tmp)
content_frame_time.gt.192 <- histogram.summary.cuts(content_frame_time.h,CUT=192)
(content_frame_time.gt.192 <- content_frame_time.gt.192[, label := "content_frame_time_192"][,])

```


```{r eval=TRUE}

allstuff <- rbindlist(
    list(
        enrollment.status,
        active.hours.cmp,
        total.hours.cmp,
        total.urisperhr.cmp,
        ncrash.all.cmp,
        ncrash.content.cmp,
        ncrash.main.cmp,
        ncrash.shutdown.cmp,
        ncrash.oom.cmp,
        ncrash.gpu.cmp,
        device.reset.cmp,
        ncrash_all.inci.cmp,
        device_resets.inci.cmp,
        checker.cmp,
        content_frame_time_vsync.gt.200,
        tab_switch_composite,
        page_load_ms,
        content_full_paint_time,
        content_full_paint_time.gt.16ms,
        content_paint_time,
        content_paint_time.99,
        content_paint_time.gt.16ms,
        composite_time,
        composite_time.gt.16ms,
        content_frame_time.gt.192
    )
)
allstuff <- cbind(date_computed = Sys.Date(),allstuff)
allstuff[, .N, by=buildid]
```


```{r eval=if(is.debug) FALSE else TRUE}

## Delete from the original table _anything_ that has buildids listed here
## which is any buildid larger than the minimum buildid we have

min_buildid <- min(allstuff$buildid)
g$q("delete from {ds_283_tablename} where buildid>='{min_buildid}'")
##system(glue("bq query --format=prettyjson --nouse_legacy_sql 'delete from {ds_283_tablename} where buildid>=\'{min_buildid}\'' "))
atemp <- tempfile()
fwrite(allstuff, file=atemp,row.names=FALSE,quote=TRUE,na=0)
l <- glue("bq load --noreplace   --project_id='{env_vars[[\'project\']]}'  --source_format=CSV --skip_leading_rows=1 --null_marker=NA",
          " \"{toShellFromSQLName(ds_283_tablename)}\" {atemp} ./dashboard_table.json")
loginfo(l)
system(l)
loginfo("Uploaded Dashboard Table")

        
        
```
